\large Neural, Tree, and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-08-01 docs/papers/sto/so.tex
FIXUP draft minor
FIXUP draft: a few sentences on training

\vspace{1em}
\subsection{Target Data and Configurations}

@@

@@

We perform parallel training using distributed GPU devices.
The training on all snapshots of a single Sobol configuration is performed on a
single GPU device.
In each training step, the loss and gradients are collected and averaged across
devices.
The SO parameters are initialized to be the same for all devices, and being
updated with the same averaged gradients.

Hyperparameters:
\YZ{
\begin{itemize}
  \item Model: number of hidden layers and nodes of f and g nets
  \item Optimization: learning rate, weight decay and dropout rate etc
\end{itemize}
}

>>>>

\vspace{1em}
\subsection{Configurations and Data for Training and Testing}

@@

\YZ{Do we give this dataset a name and release it? This could be useful for
future training projects.}

@@

We perform distributed data-parallel training using GPU devices hosted on
multiple CPU nodes.
% TODO hardware details
The 512 training data samples are uniformly distributed to the processes, with
each process being binded to a single GPU device.
In each training step, a data sample is fed into the GPU from the CPU memory
where the preloading takes place to save the reading time from the disk.

The loss and gradients are collected and averaged across the GPU devices.
The SO parameters are initialized to be the same for all devices, and being
updated with the same averaged gradients.

Hyperparameters:
\YZ{
\begin{itemize}
  \item Model: number of hidden layers and nodes of f and g nets
  \item Optimization: learning rate scheduler, weight decay and dropout rate etc
  \item Loss: fields to include and loss function forms
\end{itemize}
}
